\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{tikz}
\pgfplotsset{compat=1.18}
\usepgfplotslibrary{groupplots}

\definecolor{bg}{HTML}{0F1117}
\definecolor{fg}{HTML}{E6EDF3}
\definecolor{muted}{HTML}{8B949E}
\definecolor{accentA}{HTML}{58A6FF}
\definecolor{accentB}{HTML}{F2CC60}
\definecolor{accentC}{HTML}{7EE787}
\definecolor{accentD}{HTML}{FF7B72}
\definecolor{panel}{HTML}{161B22}
\pagecolor{bg}
\color{fg}

\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\title{SM89 Frontier Monograph Synthesis}
\author{YSU-Engine SASS RE Corpus}
\date{March 2026}

\begin{document}
\maketitle

\begin{abstract}
This monograph distills the current SM89 reverse-engineering frontier into a
bounded Ada-only evidence set. The broad inventory frontier is largely closed,
while the residual high-value frontiers are byte-qualified \texttt{P2R.B*} form
selection and \texttt{UPLOP3.LUT} semantic classification. The document uses a
single processed-data archive as the source of truth for the prose and plots.
\end{abstract}

\section{Definitions}
Let $F_T$ denote direct source/IR selection of target opcode family $T$,
$G_T$ denote local cubin-side opcode validity, and $H_T$ denote semantic
deviation under a tested pattern family. The core separation is:
\[
F_T \neq G_T \neq H_T.
\]

\section{Inventory Compression}
\pgfplotstableread[col sep=comma]{../processed/monograph_20260323/inventory_plot.csv}\inventorytable
\input{fig_inventory_closure.tex}

\section{The P2R Frontier}
\pgfplotstableread[col sep=comma]{../processed/monograph_20260323/p2r_frontier_plot.csv}\pTwoRTable
\begin{lemma}
Reproducing a neighborhood and reproducing a specific selected opcode form are
not equivalent events.
\end{lemma}

\begin{theorem}
On the current SM89 stack, the residual \texttt{P2R.B*} problem is a
form-selection problem rather than an opcode-existence problem.
\end{theorem}

\input{fig_p2r_frontier.tex}

\section{The UPLOP3 Frontier}
\pgfplotstableread[col sep=comma]{../processed/monograph_20260323/uplop3_runtime_class_counts.csv}\runtimeclass
\pgfplotstableread[col sep=comma]{../processed/monograph_20260323/uplop3_live_site_numeric.csv}\livesites
\pgfplotstableread[col sep=comma]{../processed/monograph_20260323/uplop3_pair_baseline_numeric.csv}\pairbase

\begin{theorem}
The structurally valid local cubin-side path for \texttt{UPLOP3.LUT} is
\texttt{PLOP3 -> UPLOP3}; \texttt{ULOP3 -> UPLOP3} is invalid.
\end{theorem}

\begin{corollary}
The local \texttt{UPLOP3} frontier is both structurally stratified and
semantically stratified.
\end{corollary}

\input{fig_uplop3_runtime.tex}

\section{Pair-Baseline Divergence}
\input{fig_pair_baseline.tex}

\section{Methodological Law}
Differential fuzzing is the primary semantic discriminator, compute-sanitizer
is the safety gate, and ncu/nsys are secondary observability channels. These
roles are not interchangeable and should not be collapsed into one scalar
notion of ``validation''.

\section{Open Gaps}
The remaining \texttt{P2R} gap is deeper form selection. The remaining
\texttt{UPLOP3} gap is direct source/IR emission and motif-sensitive widening
from the strongest live anchors.

\end{document}
